---
title: "Mini Data-Analysis Deliverable 1"
output: github_document
---

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

<!-- -->

    install.packages("devtools")
    devtools::install_github("UBC-MDS/datateachr")

2.  Load the packages below.

```{r}
library(datateachr)
library(tidyverse)
library(dplyr)
library(cowplot)
```

3.  Make a repository in the <https://github.com/stat545ubc-2022> Organization. You will be working with this repository for the entire data analysis project. You can either make it public, or make it private and add the TA's and Lucy as collaborators. A link to help you create a private repository is available on the #collaborative-project Slack channel. 

# Instructions

## For Both Milestones

-   Each milestone is worth 45 points. The number of points allocated to each task will be annotated within each deliverable. Tasks that are more challenging will often be allocated more points.

-   10 points will be allocated to the reproducibility, cleanliness, and coherence of the overall analysis. While the two milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as two chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

## For Milestone 1

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-1.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work below --->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to the mini-analysis GitHub repository you made earlier, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 45 points: 43 for your analysis, 1 point for having your Milestone 1 document knit error-free, and 1 point for tagging your release on Github.

# Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

# Task 1: Choose your favorite dataset (10 points)

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

-   We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

-   Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

<!-------------------------- Start your work below ---------------------------->
## The four selected datasets
Among the 7 semi-tidy datasets, we will select 4 which we will be examining further for this data analysis project. 

1: apt_buildings
2: flow_sample
3: parking_meters
4: cancer_sample
<!----------------------------------------------------------------------------->

1.2 One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->
## Exploring the datasets
To explore the datasets, we will be using the functions *glimpse* and *class* to find out at least *3* attributes (number of rows, number of columns, and the class type) about each of these datasets. As the name suggests, the *dplyr* function *glimpse* shows a glimpse of the dataset you are working with. Beyond the number of rows and columns, it also shows you the name of columns and what the data will look like. The function *class* helps reveal the class type for the dataset. 

### apt_buildings
```{r}
### EXPLORE HERE ###
glimpse(apt_buildings)
class(apt_buildings)
```
The attributes of the **apt_buildings** dataset are: 3,455 rows, 37 columns, and it was originally a data.frame that has been coerced into a tibble. 

### flow_sample
```{r}
glimpse(flow_sample)
class(flow_sample)
```
The attributes of the **flow_sample** dataset are: 218 rows, 7 columns, and it was originally a data.frame that has been coerced into a tibble. 

### parking_meters
```{r}
glimpse(parking_meters)
class(parking_meters)
```
The attributes of the **parking_meters** dataset are: 10,032 rows, 22 columns, and it was originally a data.frame that has been coerced into a tibble. 


### cancer_sample 
```{r}
glimpse(cancer_sample)
class(cancer_sample)
```
The attributes of the **cancer_sample** dataset are: 569 rows, 32 columns, and it was originally a data.frame that has been coerced into a tibble. 
<!----------------------------------------------------------------------------->

1.3 Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 2. What lead you to choose these 2? Briefly explain your choices below, and feel free to include any code in your explanation.

<!-------------------------- Start your work below ---------------------------->
## Narrowing Down to 2 Datasets
After getting a brief understanding of the datasets, we will narrow down to 2 datasets. 

### Selected datasets
**apt_buildings** & **cancer_sample**

### Explanation of Choices  
Both of these datasets are the most similar to datasets I am familiar working with and will continue to work with for my thesis.  
My previous datasets have a mix of categorical and numerical variables (similar to the apt_buildings). 
My previous datasets typically have many different columns and different parameters to consider (similar to cancer_sample). 
<!----------------------------------------------------------------------------->

1.4 Time for the final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with each dataset. Note them down below, and make your final choice based on what seems more interesting to you!

<!-------------------------- Start your work below ---------------------------->
## Final Decision 
apt_buildings: Does the number of units in a building influence the number of acessible parking spaces? 
cancer_sample: What is the relationship between radius and texture mean? 

The most interesting dataset is the **apt_buildings**.  
<!----------------------------------------------------------------------------->

# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. Remember, marks will be awarded for completion of the 4 tasks, but 10 points of the whole project are allocated to a reproducible and clean analysis. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.

# Task 2: Exploring your dataset (15 points)

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. Use *dplyr* and *ggplot*.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

<!-------------------------- Start your work below ---------------------------->
## Diving Deeper into the Data 
Here, we will go more in-depth of the naming of the graphs and functions used to get a better idea of how we can further explore our dataset. The purpose of this exercise is visualize the dataset by comparing different parameters and using different *ggplot* functions so we can develop *4* research questions. We will complete *4 out of the 8 tasks* to explore our data. 

### 1st selected task: Plotting the distribution of a numeric variable. 
We will name this plot *unts_dstrbtn*. We will do this using the *ggplot* and *geom_histogram* function. We will be examining the **no_of_units** distribution to see if there is variability of this parameter. If there is not a notable spread, then it wouldn't be worth examining how this variable relates to another. 
```{r}
unts_dstrbtn <- ggplot(apt_buildings, aes(x=no_of_units)) + geom_histogram()
print(unts_dstrbtn)
```

It is always good practice to **name our plots** rather than simply outputting them onto the file. This will make it much easier to come back to this plot later if we need to add another geom layer for example. Since we are naming the plot, we will need to use the function *print* to display the plot onto the file after we have knitted. Another helpful practice is to **remove vowels** from long variable names to shorten them. 

### 2nd selected task: Explore the relationship between 2 variables in a plot. 
We will name this plot *unts_prkng_plt*. We will be using the *ggplot* and *geom_point* function. We will be examining the relationship between **no_of_units** and **no_of_accessible_parking_spaces** because this was the original research question I had written down in 1.4. 
```{r}
unts_prkng_plt <- ggplot(apt_buildings, aes(x=no_of_units, y=no_of_accessible_parking_spaces)) + geom_point() 
print(unts_prkng_plt)
```

Upon examination of the plot, it is clear that **one** apartment has 4000 units, which makes it difficult to examine the relationship. Therefore, using the *filter* function, we will remove this outlier and then plot the remaining apartments. We will name this new plot *unts_prkng_n4K_plt*

```{r}
unts_prkng_n4K_plt <- apt_buildings %>% 
  # remove the apartment with <4000 units 
  filter(no_of_units<4000) %>%
  ggplot(aes(x=no_of_units, y=no_of_accessible_parking_spaces)) + geom_point() 
print(unts_prkng_n4K_plt)
```

Here, we used the pipe (*%>%*) to condense our code. This can be interpreted as "and then" as you are reading the code. This approach above is a condense and successful approach in plotting the number of units against the number of accessible parking spaces while omitting the 4000 unit outlier. Using a pipe is best when calling multiple functions, as it can combine them into a single statement. This is preferred approach to creating an entirely new dataset and then making the plot on a separate chunk of code, like below:

```{r}
# Creating a separate dataset which filters out the outlier
apt_buildings_no4K <- filter(apt_buildings, no_of_units<4000)
# Plot using the newly made dataset  
unts_prkng_n4K_plt_2 <- ggplot(apt_buildings_no4K, aes(x=no_of_units, y=no_of_accessible_parking_spaces)) + geom_point() 
print(unts_prkng_n4K_plt_2)
```

As you can see, both approaches produce the exact same plot, but the former is preferred given its conciseness and prevents you from cluttering your workspace.

### 3rd selected task: Use a boxplot to look at the frequency of different observations within a single variable.
We will name this plot *units_property_boxplot*. We will be do this using the *ggplot* and *geom_boxplot* function. We will examine the no_of_units and property_type variables. This helps to see if the property type will impact the number of units. Once again, we will omit the apartment with 4000 units. 
```{r}
parking_property_boxplot <- ggplot(apt_buildings_no4K, aes(property_type, no_of_units)) + geom_boxplot(width=0.2) 
print(parking_property_boxplot)
```

### 4th selected task: Use a density plot to explore any of your variables 
We will name this plot *Acc_parking_density*. We will be using the *ggplot* and *geom_density* functions. Similar to to plotting the distribution of the units, this will allow us to see if there is enough of a spread of this variable to see its relation to another parameter. 
```{r}
Acc_parking_density <- ggplot(apt_buildings, aes(x=no_of_accessible_parking_spaces)) + geom_density()
print(Acc_parking_density)
```
<!----------------------------------------------------------------------------->


# Task 3: Write your research questions (5 points)

So far, you have chosen a dataset and gotten familiar with it through exploring the data. Now it's time to figure out 4 research questions that you would like to answer with your data! Write the 4 questions and any additional comments at the end of this deliverable. These questions are not necessarily set in stone - TAs will review them and give you feedback; therefore, you may choose to pursue them as they are for the rest of the project, or make modifications!

<!--- *****START HERE***** --->
1. How does the age of the apartment (based on year built) impact the apartment's presence of emergency power?
2. How does property type influence the number of stories in an apartment, and the relationship between stories and units? 
3. Are the differences between apartment age (based on year built) that allow and don't allow pets? 
4. How does the number of units impact the apartment's visitor parking availability? 


# Task 4: Process and summarize your data (13 points)

From Task 2, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions.

### 1.1 (10 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4.  Based on two categorical variables, calculate two summary statistics of your choosing.

**Graphing:**

5.  Create a graph out of summarized variables that has at least two geom layers.
6.  Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7.  Make a graph where it makes sense to customize the alpha transparency.
8.  Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->
#### Research Question 1 
How does the age of the apartment (based on year built) impact the apartment's presence of emergency power? 

##### Summarizing Task 
Computing the *range*, *mean*, *median*, and *standard deviation* of the *year_built* across the *emergency_power* categorical variable. 

Using the *range* function will output a vector made of two numbers (the lowest and highest value among the selected column). Unfortunately, I was not able to output both ranges (the year built for apartments with and without emergency power) in a single statement. Additionally, the *range* function only works if we call on a numeric vector, which makes it difficult to execute this task without creating a separate dataset. Using comments within the code, I will outline the steps for apartments that do have emergency power ("YES" under the *emergency_power* column) below. 

**Apartments with Emergency Power - Year Built - Range:** 
```{r}
# filter the dataset so it only has apartments with emergency power
emerg_pwr_ys <- filter(apt_buildings, emergency_power=="YES" )

# find the range of year_built across this new dataset
emerg_pwr_ys_rng <- range(emerg_pwr_ys$year_built, na.rm = TRUE)
print(emerg_pwr_ys_rng)
```
The *$* function allows us to access a particular variable in a dataset. In this context, we were accessing the *year_built* variable within the *emerg_pwr_ys* dataset to find the range. The *na.rm = TRUE* ensures that NA values are omitted (by default, the *range* function sets this to FALSE). 

We can use the same process for apartments that do not have emergency power.

**Apartments without Emergency Power - Year Built - Range:** 
```{r}
# filter the dataset so it only has apartments without emergency power
emerg_pwr_no <- filter(apt_buildings, emergency_power=="NO" )

# calculate and print the range of year_built across this new dataset
emerg_pwr_no_rng <- range(emerg_pwr_no$year_built, na.rm = TRUE)
print(emerg_pwr_no_rng)
```

To find the *mean, standard deviation (sd), and median*, we will summarize these values into a table for seamless comparison between the two types of apartments. 

**Emergency Power Summary - Year Built - Mean, SD, Median:** 
```{r}
# mean, sd, median
yr_blt_smmry <- apt_buildings %>% 
  # remove rows where emergency_power is NA 
  filter(!is.na(emergency_power)) %>%
  group_by(`emergency_power`) %>%
  summarise(year_mean = mean(year_built, na.rm = TRUE), year_sd=sd(year_built, na.rm= TRUE), year_median=median(year_built, na.rm=TRUE))
print(yr_blt_smmry)
```

**Why this task helps:** This summarizing task helps demonstrate the relationship between year an apartment was built and the presence of an emergency room. On average, buildings with emergency power were built more recent than those without emergency power. 

##### Graphing Task
Create a graph out of summarized variables (*year_built* and *visitor_parking*) that has at least two geom layers (*geom_point* and *geom_boxplot*).

**Emergency Power and Year Built - Box Plot**
```{r}
yr_blt_vstr_prkng <- apt_buildings %>%
  # remove the rows where visitor_parking is NA
  filter(!is.na(emergency_power)) %>%
  ggplot(aes(emergency_power, year_built)) + geom_boxplot(width=0.2) + geom_point() 
print(yr_blt_vstr_prkng)
```

**Why this task helps:** This graphing tasks helps show that the year built does have an influence on the type of visitor parking. The medians (indicated by the horizontal black line) are slightly different. This graph also helps us see the high variability for year built with the both types of apartments (with and without emergency power)

#### Research Question 2
How does property type influence the number of stories in an apartment, and the relationship between stories and units? 

##### Summarizing Task 
Computing the *range*, *mean*, *median*, and *standard deviation* of the *no_of_storeys* numerical variable across the *property_type* categorical variable.

Similar to the summarizing task for **Research Question 1**, we will separate the *range* operation for each *property type* category. 

**PRIVATE - Number of Storeys - Range:**
```{r}
# filter the dataset so it only has PRIVATE apartments 
prprty_typ_prvt <- filter(apt_buildings, property_type=="PRIVATE" )

# calculate and print the range of no_of_storeys across this new dataset
prprty_typ_prvt_rng <- range(prprty_typ_prvt$no_of_storeys, na.rm = TRUE)
print(prprty_typ_prvt_rng)
```

**SOCIAL HOUSING - Number of Storeys - Range:** 
```{r}
# filter the dataset so it only has SOCIAL HOUSING apartments 
prprty_typ_scl_hsng <- filter(apt_buildings, property_type=="SOCIAL HOUSING" )

# calculate and print the range of no_of_storeys across this new dataset
prprty_typ_scl_hsng_rng <- range(prprty_typ_scl_hsng$no_of_storeys, na.rm = TRUE)
print(prprty_typ_scl_hsng_rng)
```

**TCHC - Number of Storeys - Range:**
```{r}
# filter the dataset so it only has TCHC apartments 
prprty_typ_TCHC <- filter(apt_buildings, property_type=="TCHC" )

# calculate and print the range of no_of_storeys across this new dataset
prprty_typ_TCHC_rng <- range(prprty_typ_TCHC$no_of_storeys, na.rm = TRUE)
print(prprty_typ_TCHC_rng)
```

Finding the *mean, sd, and median* will follow the same process as **Research Question 1**.

**Property Type Summary - Number of Storeys - Mean, SD, Median:** 
```{r}
# mean, sd, median
prprty_typ_smmry <- apt_buildings %>% 
  group_by(`property_type`) %>%
  summarise(storey_mean = mean(no_of_storeys, na.rm = TRUE), storey_sd=sd(no_of_storeys, na.rm= TRUE), storey_median=median(no_of_storeys, na.rm=TRUE))
print(prprty_typ_smmry)
```

**Why this task helps:** This summarizing task helps us show that the property type does not greatly influence the number of stories in the apartment as the means range from 6-9. However, it suggests that TCHC typically has the most stories and Private ones have the lowest.

##### Graphing Task 
Create a graph out of summarized variables (*no_of_storeys* and *no_of units*, separated by *property_type*) that has at least two geom layers (*geom_point* and *geom_smooth*). To create separate figures (per property type) we use the *facet_wrap* function. 

**Number of Storeys, Number of Units and Property Type - Group Plot** 
```{r}
strys_unts_prpty <- apt_buildings %>% 
  # remove the apartment with <4000 units 
  filter(no_of_units<4000) %>%
  ggplot(aes(no_of_storeys, no_of_units)) + facet_wrap(~property_type) + geom_point() + geom_smooth()
print(strys_unts_prpty)
```


**Why this task helps:** This graphing task helps show that a linear relationship between the number of stories and the number of units is generally maintained across all three property types. 

#### Research Question 3
Are the differences between apartment age (based on year built) that allow and don't allow pets? 

##### Summarizing task
Compute the number of observations for at least one of your categorical variables (*pets_allowed*). Do not use the function `table()`! We can use the *count* function to accomplish this task.

**Pets Allowed - Count** 
```{r}
pets_count <- apt_buildings %>%
  # remove the rows where pets_allowed is NA
  filter(!is.na(pets_allowed)) %>%
  count(pets_allowed)
print(pets_count)
```

**Why this task helps:** This summarizing task helps show how many buildings allow and don't allow pets. This helps understand if there are enough apartments for each category ("yes" or "no") to compare the two types of apartments. 

##### Graphing task
Create a graph out of summarized variables (*year_built* and *pets_allowed*) that has at least two geom layers (*geom_point* and *geom_boxplot*).

**Pets Allowed and Year Built - Box Plot**    
```{r}
pts_allwd_yr_blt <- apt_buildings %>%
  # remove the rows where pets_allowed is NA
  filter(!is.na(pets_allowed)) %>%
  ggplot(aes(pets_allowed, year_built)) + geom_boxplot(width=0.2) + geom_point() 
print(pts_allwd_yr_blt)
```

**Why this task helps:** This graph shows that there is not much of a difference between the year built and its allowance of pets. In other words, the year built does not influence the pet allowance in an apartment. This is also helpful for research question 1. 

#### Research Question 4
How does the number of units impact the apartment's visitor parking availability? 

##### Summarizing Task
Computing the *range*, *mean*, *median*, and *standard deviation* of the number of apartments across the *visitor_parking* categorical variable. 

**BOTH range:** 
```{r}
# filter the dataset so it only has apartments with both visitor parkings
vstr_prkng_bth <- filter(apt_buildings, visitor_parking=="BOTH" )

# calculate and print the range of no_of_units across this new dataset
vstr_prkng_bth_rng <- range(vstr_prkng_bth$no_of_units, na.rm = TRUE)
print(vstr_prkng_bth_rng)
```

**FREE range:** 
```{r}
# filter the dataset so it only has apartments with free visitor parkings
vstr_prkng_fr <- filter(apt_buildings, visitor_parking=="FREE")

# calculate and print the range of no_of_units across this new dataset
vstr_prkng_fr_rng <- range(vstr_prkng_fr$no_of_units, na.rm = TRUE)
print(vstr_prkng_fr_rng)
```

**PAID range:**  
```{r}
# filter the dataset so it only has apartments with paid visitor parkings
vstr_prkng_pd <- filter(apt_buildings, visitor_parking=="PAID")

# calculate and print the range of no_of_units across this new dataset
vstr_prkng_pd_rng <- range(vstr_prkng_pd$no_of_units, na.rm = TRUE)
print(vstr_prkng_pd_rng)
```

**UNAVAILABLE range:** 
```{r}
# filter the dataset so it only has apartments with free visitor parkings
vstr_prkng_unvlbl <- filter(apt_buildings, visitor_parking=="UNAVAILABLE")

# calculate and print the range of no_of_units across this new dataset
vstr_prkng_unvlbl_rng <- range(vstr_prkng_unvlbl$no_of_units, na.rm = TRUE)
print(vstr_prkng_unvlbl_rng)
```

**Visitor Parking Summary - Number of Units - Mean, SD, Median:** 
```{r}
# mean, sd, median
no_unts_smmry <- apt_buildings %>% 
  # remove rows where visitor_parking is NA 
  filter(!is.na(visitor_parking)) %>%
  group_by(`visitor_parking`) %>%
  summarise(no_unit_mean = mean(no_of_units, na.rm = TRUE), no_unit_sd=sd(no_of_units, na.rm= TRUE), no_unit_median=median(no_of_units, na.rm=TRUE))
print(no_unts_smmry)
```
**Why this task helps:** This summarizing task helps show how the number of units vary between visitor parking status. We can see that the unavailable visiting parking had the lowest number of units and the highest number of units offered both kinds of visitor parking. 
 
##### Graphing Task
Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best. 
We can use the *geom_histogram* function to make our historgrams, and edit the *binwidth* to adjust the size of bins. We can display all of these plots together using the *plot_grid* function from the *cowplot* library. 

**Visitor Parking and Number of Units - Filled Histograms** 
```{r}
unit_hist_bin1 <- apt_buildings %>%
  # remove the apartments with <4000 units and visitor parking is NA
  filter(no_of_units<4000 & !is.na(visitor_parking)) %>%  
  ggplot(aes(no_of_units, fill=visitor_parking)) + geom_histogram(binwidth = 1)

unit_hist_bin5 <- apt_buildings %>%
  # remove the apartments with <4000 units and visitor parking is NA
  filter(no_of_units<4000 & !is.na(visitor_parking)) %>%  
  ggplot(aes(no_of_units, fill=visitor_parking)) + geom_histogram(binwidth = 5)

unit_hist_bin10 <- apt_buildings %>%
  # remove the apartments with <4000 units and visitor parking is NA
  filter(no_of_units<4000 & !is.na(visitor_parking)) %>%  
  ggplot(aes(no_of_units, fill=visitor_parking)) + geom_histogram(binwidth = 10)


combined_hist <- plot_grid(unit_hist_bin1, unit_hist_bin5, unit_hist_bin10, nrow = 3, labels = "AUTO")

print(combined_hist)
```

Among the 3 histograms (A = bin-width 1, B = bin-width 5, C = bin-width 10), the bin-width of 10 is the 'best' one because it has the best balance of spreading the bars both horizontally and vertically across the graph.

```{r}
print(unit_hist_bin10)
```

**Why this task helps:** This histogram shows how the visitor parking status can vary based on the number of units. For example, this graph helps show that Free visitor parking seems to be present in greater relative proportions as the number of units increase. 


### 1.2 (3 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!-------------------------- Start your work below ---------------------------->
The operations have helped me come closer to answering my research questions as we can see if there are relationships between different parameters. For example, we know that the year that an apartment is built has a slight impact on whether there is emergency power or not. Additionally, the number of units may influence the type of visitor parking available. On the other hand, there are a similar number of stories across different property types and the allowance of pets does not seem to be affected by the apartment's age (based on year built). There aren't any aspects of the research questions that remain unclear, but this is likely because the questions were fairly specific. Therefore, I may need to revise these questions so they cover a broader topic (but, I will wait for the TA's feedback). The most interesting results were the very notable differences between mean number of units across different property type (research question 4). 
<!----------------------------------------------------------------------------->

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.